---
title: "AnalysisDocument_draft"
output: pdf_document
date: "2024-06-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(knitr)
library(stringr)
```

# Introduction

This report presents the results of microplastics analysis conducted using Fourier-transform infrared spectroscopy (FTIR) at the Moore Institute for Plastic Pollution Research. The analysis includes the number of particles per sample, their size, shape, and polymer type.

# Data Summary

```{r data-summary}
# Load the dataset (assuming the dataset is named 'microplastics_data.csv')
microplastics_data <- read.csv("particle_details_all.csv")
mp_data <- microplastics_data %>%
  filter(bad_spectra == "FALSE" & material_class != "unknown")
mp_data$sample_id = str_sub(mp_data$sample_id,1,nchar(mp_data$sample_id)-4)

# Display the first few rows of the dataset
head(mp_data)
```

# Number of Particles per Sample

```{r particles-per-sample}
# Summarize the number of particles per sample
particles_per_sample <- mp_data %>%
  group_by(sample_id) %>%
  summarize(Num_Particles = n())

# Display the summary table
kable(particles_per_sample, caption = "Number of Particles per Sample")

# Plot the number of particles per sample
ggplot(particles_per_sample, aes(x = sample_id, y = Num_Particles)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Particles per Sample", x = "Sample", y = "Number of Particles") +
  theme_minimal()
```

# Particle Size Distribution

```{r particle-size-distribution}
# Summarize the particle size distribution
particle_size_distribution <- microplastics_data %>%
  group_by(Size) %>%
  summarize(Count = n())

# Display the summary table
kable(particle_size_distribution, caption = "Particle Size Distribution")

# Plot the particle size distribution
ggplot(particle_size_distribution, aes(x = Size, y = Count)) +
  geom_bar(stat = "identity") +
  labs(title = "Particle Size Distribution", x = "Size", y = "Count") +
  theme_minimal()
```

# Particle Shape Distribution

```{r particle-shape-distribution}
# Summarize the particle shape distribution
particle_shape_distribution <- microplastics_data %>%
  group_by(Shape) %>%
  summarize(Count = n())

# Display the summary table
kable(particle_shape_distribution, caption = "Particle Shape Distribution")

# Plot the particle shape distribution
ggplot(particle_shape_distribution, aes(x = Shape, y = Count)) +
  geom_bar(stat = "identity") +
  labs(title = "Particle Shape Distribution", x = "Shape", y = "Count") +
  theme_minimal()
```

# Polymer Type Distribution

```{r polymer-type-distribution}
# Summarize the polymer type distribution
polymer_type_distribution <- microplastics_data %>%
  group_by(Polymer_Type) %>%
  summarize(Count = n())

# Display the summary table
kable(polymer_type_distribution, caption = "Polymer Type Distribution")

# Plot the polymer type distribution
ggplot(polymer_type_distribution, aes(x = Polymer_Type, y = Count)) +
  geom_bar(stat = "identity") +
  labs(title = "Polymer Type Distribution", x = "Polymer Type", y = "Count") +
  theme_minimal()
```

# Conclusion

This report provides a detailed analysis of the microplastics collected and analyzed using FTIR. The data includes the number of particles, their size, shape, and polymer type, which are crucial for understanding the extent and nature of microplastic pollution.

```

Replace `"microplastics_data.csv"` with the actual path to your dataset file. This R Markdown document will generate an HTML report with summaries and visualizations of the microplastics analysis data.